Language Bias in a Multilingual Tweet Corpus

### 2018-06-27 paper.tex
Merge

>>>>

The tweets were written by \hl{41\,170} users. We refer to a user who produced at least 50 tweets as an \textit{active user}. There are \hl{2\,766} (\hl{6.7\%}) active users who produced \hl{1,196,558} (\hl{86.6\%}) tweets in total.

Among active users, \hl{789} are monoligual. Exclusively in Latvian write \hl{631} (\hl{80.0\%}), in Russian \hl{40} (\hl{5.1\%}) and in English \hl{118} (\hl{15.0\%}).
